Charity analysis

### 2022-07-17 Shiny/Test/Flexdashboard test.Rmd
Title and comments.

---
title: "Untitled"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
runtime: shiny
---

@@

# Function to read Excel file
widen_excel <- function(file){
    read_excel(file) |> 
      mutate(
        Value = Value * 1000
      ) |> 
      unite(
        entry, c(Category, Name), sep = "_"
      ) |> 
      select(-`Sub-category`) |> 
      pivot_wider(names_from = entry, values_from = Value) |> 
      clean_names()
}
```

@@

observeEvent(input$click, { # wait for button click

@@

### Chart B

@@

### Chart C
```{r}
plotOutput("htmlplot")
```

>>>>

---
title: "Charity analysis"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
runtime: shiny
---

@@

# Function to read Excel file
widen_excel <- function(file){
    read_excel(file) |> 
      mutate(
        Value = Value * 1000
      ) |> 
      unite(
        entry, c(Category, Name), sep = "_"
      ) |> 
      select(-`Sub-category`) |> 
      pivot_wider(names_from = entry, values_from = Value) |> 
      clean_names()
}

# Shiny actions
observeEvent(input$click, { # wait for button click

@@

```

@@

### Plotly

@@

### ggplot
```{r}
plotOutput("htmlplot")
```
